---
title: "RECODE GLES Panel"
subtitle: "Political Efficacy vs. AfD- Fully Contrained Models"
author:
- "Reimar ZEH"
- "[Lehrstuhl für Kommunikationswissenschaft](https://www.kowi.rw.fau.de)"
- "Filename: *Recode ZA6838-ZA7729*"
date: "`r format(Sys.time(), '%m.%d.%Y')`"
editor: source
toc: true
number-sections: true
highlight-style: pygments
theme: cosmo
format:
  html: 
    code-fold: true
    code-overflow: wrap
    html-math-method: katex
    self-contained: true
execute: 
  echo: false
  eval: true
  warning: false
editor_options: 
  chunk_output_type: console
---

# Session Setup

## Global settings & Notes

```{r}
rm(list= ls()) # start clean ####
# show chunk outputs in R-Markdown
knitr::opts_chunk$set(echo = TRUE)

# global settings
options(
  scipen = 999, # deactivate scientific notation
  digits = 3, # activate the required number of decimal places
  max.print = 1000000,
  tibble.print_max = 100000,
  tibble.print_min = 100000
)

# setting a seed
set.seed(42)
```

## Load Packages

```{r}
rm(list= ls()) # start clean ####
if (!require("pacman")) install.packages("pacman")
pacman::p_load(sjlabelled,foreign,tidyverse,sjmisc,Hmisc,flextable,
               here,fs,usethis,labelled,janitor,magrittr,qs,tictoc,
               psych,easystats,irr,lavaan,semTools,semPlot,broom)
```

## Prepare Lists

```{r}
DF = list()
```

## Load Data

```{r}
# load(paste0(Sys.getenv("FAUBOX"),"/GLES/za6838/za6838_7729.Rda"))
# tic()
DF$orgdat = qread(paste0(Sys.getenv("FAUBOX"),"/GLES/za6838/za6838_7729.qs"))
source(here("script/models.R"))
# toc()
```


# Prepare Analysis
## Select Vars
```{r}
DF$semdat_1 = DF$orgdat %>% select(contains(c("_430i","_050a","_050e","_050h","_050k")) & starts_with(c("kp14","kp15","kp16","kp17","kp18")) & !ends_with("be"))
head(DF$semdat_1)
# DF$semdat_1_long = DF$semdat_1 %>% pivot_longer(cols = everything(), names_to = c("set",".value"), names_sep = "_")
# head(DF$semdat_1_long)
# names(DF$semdat_1_long) = c("Welle","m","w")


```



## Check FRQ
```{r}
# tic()
DF$semdat_1 %>% summary(.,maxsum = 20) %>% knitr::kable(.,format= 'markdown')
# toc()
```


## Check Correlations
```{r}
DF$semdat_1 %>% mutate(across(everything(), ~rec(., rec = "-99,-97,-95,-93=NA;else = copy"))) %>%
  psych::cor.plot(.,stars = T)

# DF$semdat_1_long %>% select(!"Welle") %>%
#   mutate(across(everything(), ~rec(., rec = "-99,-97,-95,-93,-92=NA;else = copy"))) %>%
#   drop_na() %>% 
#   psych::corr.test()
# DF$semdat_1 %>% mutate(across(everything(), ~rec(., rec = "-99,-97,-95,-93,-92=NA;else = copy"))) %>%
#   gather(key, value) %>% drop_na() %>% 
#   separate_wider_delim(key, delim = "_", names = c("Welle", "Var")) %>%
#   ggplot(aes(x = value, color = Welle)) +
#   geom_density(adjust = 1.6) + 
#   facet_wrap(vars(Var)) + 
#   theme_classic()
```

# Factor Analysis
## Prepare Data {.unlisted .unnumbered}
```{r}
#| echo: false
#| include: false

DF$w14_efa = DF$semdat_1 %>% select(ends_with(c("_050a","_050e","_050h","_050k"))) %>%
  mutate(across(everything(), ~rec(., rec = "-99,-97,-95,-93=NA;else = copy")))
```

## Preliminary Analyse {.unlisted .unnumbered}
```{r}
#| echo: false
#| include: false
parameters::n_factors(DF$w14_efa) %>% knitr::kable(.,format= 'markdown')
DF$w14_efa %>% summary(.,maxsum = 20) %>% knitr::kable(.,format= 'markdown')
DF$w14_efa %>% psych::cor.plot(.,stars = T)
DF$w14_efa.fa = fa(DF$w14_efa, nfactors = 2, fm = "ml", rotate = "oblimin", scores = "regression", use = "pairwise.complete.obs")
DF$w14_efa.fa %>% model_parameters(sort=T, threshold = "max") %>% knitr::kable(.,format= 'markdown')
DF$w14_effi = factor.scores(DF$w14_efa,DF$w14_efa.fa)
DF$semdat_1 %>% mutate(across(everything(), ~rec(., rec = "-99,-95,-93,-92=NA; else = copy"))) %>%
  psych::cor.plot(.,stars = T)

```

## Perform Analysis

```{r}
DF$kp14_eff_pca = DF$semdat_1 %>% select(starts_with("kp14") & contains("_050")) %>% 
  mutate(across(everything(), ~rec(., rec = "-99,-95,-93,-92=NA; else = copy"))) %>%
  principal_components(.,rotation = "oblimin", n = 2) %>% get_scores() %>%
  rename(kp14_exef = Component_1, kp14_inef = Component_2)
DF$kp15_eff_pca = DF$semdat_1 %>% select(starts_with("kp15") & contains("_050")) %>% 
  mutate(across(everything(), ~rec(., rec = "-99,-95,-93,-92=NA; else = copy"))) %>%
  principal_components(.,rotation = "oblimin", n = 2) %>% get_scores() %>%
  rename(kp15_exef = Component_1, kp15_inef = Component_2)
DF$kp16_eff_pca = DF$semdat_1 %>% select(starts_with("kp16") & contains("_050")) %>% 
  mutate(across(everything(), ~rec(., rec = "-99,-95,-93,-92=NA; else = copy"))) %>%
  principal_components(.,rotation = "oblimin", n = 2) %>% get_scores() %>%
  rename(kp16_exef = Component_1, kp16_inef = Component_2)
DF$kp17_eff_pca = DF$semdat_1 %>% select(starts_with("kp17") & contains("_050")) %>% 
  mutate(across(everything(), ~rec(., rec = "-99,-95,-93,-92=NA; else = copy"))) %>%
  principal_components(.,rotation = "oblimin", n = 2) %>% get_scores() %>%
  rename(kp17_exef = Component_1, kp17_inef = Component_2)
DF$kp18_eff_pca = DF$semdat_1 %>% select(starts_with("kp18") & contains("_050")) %>% 
  mutate(across(everything(), ~rec(., rec = "-99,-95,-93,-92=NA; else = copy"))) %>%
  principal_components(.,rotation = "oblimin", n = 2) %>% get_scores() %>%
  rename(kp18_exef = Component_1, kp18_inef = Component_2)
# Rebind DATA
DF$semdat_1 = cbind(DF$semdat_1,DF$kp14_eff_pca,DF$kp15_eff_pca,DF$kp16_eff_pca,DF$kp17_eff_pca,DF$kp18_eff_pca)
```




## Check ICC
```{r}
# ICC requires VARs to be numeric, even when they seem to are numeric -> mutate!

DF$semdat_1 %>% select(contains(c("_020"))) %>% 
                         mutate(across(everything(), ~rec(., rec = "-99,-95,-93=NA; else = copy"))) %>% irr::icc()
DF$semdat_1 %>% select(contains(c("_exef"))) %>% irr::icc()
DF$semdat_1 %>% select(contains(c("_inef"))) %>% irr::icc()
```


# SEM
## Prepare VARS
```{r}
DF$semdat_1 %<>% select(contains(c("_020","_exef")) & starts_with(c("kp14","kp15","kp16","kp17","kp18"))) %>% 
  mutate(across(everything(), ~rec(., rec = "-99,-95,-93=NA;-97=1;else = copy")))

names(DF$semdat_1)<- c("m1", "m2", "m3", "m4", "m5","w1", "w2", "w3", "w4", "w5")

# DF$semdat_1 %>% summary(.,maxsum = 20) %>% knitr::kable(.,format= 'markdown')
```

## CLPM Latent
```{r}
DF$int_smL.fit <- lavaan::sem(DF$clpm_L5, data=DF$semdat_1, missing="ML", estimator = "MLR", mimic="Mplus", meanstructure = "default")
broom::glance(DF$int_smL.fit) %>% select(., c(cfi,tli,agfi,rmsea,srmr,AIC,BIC)) %>% mutate(across(where(is.double), round, 3)) %>% knitr::kable(.,format= 'markdown')
broom::tidy(DF$int_smL.fit) %>% filter(., label!="") %>% mutate(across(where(is.double), round, 3)) %>% 
  select(., c(term, label, op, estimate,std.error,p.value,std.all)) %>% 
  flextable() %>% theme_zebra() %>% 
  color(., i = ~ p.value < 0.05,j = ~ term + p.value + std.all, color="blue") %>%
  bold(., i = ~ p.value < 0.05 & op == "~",j = ~ term + p.value + std.all, bold=T) %>% autofit()
semPaths(DF$int_smL.fit, what = "std", whatLabels="std", layout="tree2", intercepts = F, residuals = T, structural = T, 
         curvePivot = T, style="mx", rotation = 2, fade = F, edge.label.cex=0.7, edge.label.position = 0.4)
title("DemZufriedenheit/External Efficacy")
```

## CLPM Latent Contrained
```{r}
DF$int_smL.fit <- lavaan::sem(DF$clpm_L5C, data=DF$semdat_1, missing="ML", estimator = "MLR", mimic="Mplus", meanstructure = "default")
broom::glance(DF$int_smL.fit) %>% select(., c(cfi,tli,agfi,rmsea,srmr,AIC,BIC)) %>% mutate(across(where(is.double), round, 3)) %>% knitr::kable(.,format= 'markdown')
broom::tidy(DF$int_smL.fit) %>% filter(., label!="") %>% mutate(across(where(is.double), round, 3)) %>% 
  select(., c(term, label, op, estimate,std.error,p.value,std.all)) %>% 
  flextable() %>% theme_zebra() %>% 
  color(., i = ~ p.value < 0.05,j = ~ term + p.value + std.all, color="blue") %>%
  bold(., i = ~ p.value < 0.05 & op == "~",j = ~ term + p.value + std.all, bold=T) %>% autofit()
semPaths(DF$int_smL.fit, what = "std", whatLabels="std", layout="tree2", intercepts = F, residuals = T, structural = T, 
         curvePivot = T, style="mx", rotation = 2, fade = F, edge.label.cex=0.7, edge.label.position = 0.4)
title("DemZufriedenheit/External Efficacy")
```

## RI-CLPM
```{r}
#| warning: false
tic()
DF$int_smR.fit <- lavaan::sem(DF$riclpm5, data=DF$semdat_1, missing="ML", estimator = "MLR", mimic="Mplus", meanstructure = "default")
broom::glance(DF$int_smR.fit) %>% select(., c(cfi,tli,agfi,rmsea,srmr,AIC,BIC)) %>% mutate(across(where(is.double), round, 3)) %>% knitr::kable(.,format= 'markdown')
broom::tidy(DF$int_smR.fit) %>% filter(., label!="") %>% mutate(across(where(is.double), round, 3)) %>% 
  select(., c(term, label, op, estimate,std.error,p.value,std.all)) %>% 
  flextable() %>% theme_zebra() %>% 
  color(., i = ~ p.value < 0.05,j = ~ term + p.value + std.all, color="blue") %>%
  bold(., i = ~ p.value < 0.05 & op == "~",j = ~ term + p.value + std.all, bold=T) %>% autofit()
semPaths(DF$int_smR.fit, what = "std", whatLabels="std", layout="tree2", intercepts = F, residuals = T, structural = T, 
         curvePivot = T, style="mx", rotation = 2, fade = F, edge.label.cex=0.7, edge.label.position = 0.4)
title("DemZufriedenheit/External Efficacy")
toc()
```

## RI-CLPM Constrained
```{r}
#| warning: false
tic()
DF$int_smR.fit <- lavaan::sem(DF$riclpm5C, data=DF$semdat_1, missing="ML", estimator = "MLR", mimic="Mplus", meanstructure = "default")
broom::glance(DF$int_smR.fit) %>% select(., c(cfi,tli,agfi,rmsea,srmr,AIC,BIC)) %>% mutate(across(where(is.double), round, 3)) %>% knitr::kable(.,format= 'markdown')
broom::tidy(DF$int_smR.fit) %>% filter(., label!="") %>% mutate(across(where(is.double), round, 3)) %>% 
  select(., c(term, label, op, estimate,std.error,p.value,std.all)) %>% 
  flextable() %>% theme_zebra() %>% 
  color(., i = ~ p.value < 0.05,j = ~ term + p.value + std.all, color="blue") %>%
  bold(., i = ~ p.value < 0.05 & op == "~",j = ~ term + p.value + std.all, bold=T) %>% autofit()
semPaths(DF$int_smR.fit, what = "std", whatLabels="std", layout="tree2", intercepts = F, residuals = T, structural = T, 
         curvePivot = T, style="mx", rotation = 2, fade = F, edge.label.cex=0.7, edge.label.position = 0.4)
title("DemZufriedenheit/External Efficacy")
toc()
```


## Save DATA, if neccessary {.unlisted .unnumbered}
```{r}
#| include: false
# DF %>% qsave(., file = paste0(Sys.getenv("FAUBOX"),"/GLES/za6838/text.qs"))
```
