---
title: "RECODE GLES Panel"
subtitle: "MediaTrust vs AfD Sympathie 2021 - 2023"
author:
- "Reimar ZEH"
- "[Lehrstuhl für Kommunikationswissenschaft](https://www.kowi.rw.fau.de)"
- "Filename: *Recode ZA6838-ZA7730*"
date: "`r format(Sys.time(), '%m.%d.%Y')`"
editor: source
toc: true
number-sections: true
highlight-style: pygments
theme: cosmo
format:
  html: 
    code-fold: true
    code-overflow: wrap
    html-math-method: katex
    self-contained: true
    page-layout: full
    grid:
      sidebar-width: 100px
      body-width: 1500px
      margin-width: 200px
      gutter-width: 1.5rem
execute: 
  echo: false
  eval: true
  warning: false
editor_options: 
  chunk_output_type: console
---

# Session Setup

## Global settings & Notes

```{r}
rm(list= ls()) # start clean ####
# show chunk outputs in R-Markdown
knitr::opts_chunk$set(echo = TRUE)

# global settings
options(
  scipen = 999, # deactivate scientific notation
  digits = 3, # activate the required number of decimal places
  max.print = 1000000,
  tibble.print_max = 100000,
  tibble.print_min = 100000
)

# setting a seed
set.seed(42)
```

## Load Packages

```{r}
rm(list= ls()) # start clean ####
if (!require("pacman")) install.packages("pacman")
pacman::p_load(sjlabelled,foreign,tidyverse,sjmisc,Hmisc,panelr,gt,gtExtras,
               here,fs,usethis,labelled,janitor,magrittr,qs,tictoc,
               psych,easystats,irr,lavaan,semTools,semPlot,broom,tidySEM)
```

## Prepare Lists

```{r}
DF = list()
```

## Load Data

```{r}
# load(paste0(Sys.getenv("FAUBOX"),"/GLES/za6838/za6838_7729.Rda"))
# tic()
DF$orgdat = qread(paste0(Sys.getenv("FAUBOX"),"/GLES/za6838/za6838_7730.qs"))
source(here("script/CLPMulder.R"))
source(here("script/RICLPMulder.R"))
# toc()
```


# Prepare Analysis
## Select Vars
```{r Select and Recode}
DF$semdat = DF$orgdat %>%
  select(ends_with(c("_160p1","_160p2","_430i")) & starts_with(c("kp21","kp23","kp24")))
descr(DF$semdat, show = c("type", "n", "range"))
```


## Recode Vars for sem
```{r}
DF$semdat = DF$semdat %>% mutate(across(everything(), ~ as_numeric(.)))
DF$semdat = DF$semdat %>% mutate(across(everything(),  ~rec(., rec = "NA=-99; else = copy")))
DF$semdat %>% descr()
# DF$semdat = DF$semdat %>% mutate(afd_max = if_any(contains("430i"), ~.x > 1)) # Alle identifizieren, die AfD nicht immer scheiße finden.


negative_indices <- which(DF$semdat < 0, arr.ind = TRUE)
DF$negvals <- DF$semdat[negative_indices] %>% as.vector() %>% unique() %>% sort()
rm(negative_indices)

go_away <- function(x, na_values) {
  x[x %in% na_values] <- NA
  return(x)
}
DF$semdat = DF$semdat %>% mutate(across(everything(), ~(go_away(., DF$negvals))))

descr(DF$semdat, show = c("type", "n", "range"))

# DF$semdat = DF$semdat %>% filter(.,afd_max==TRUE) # Alle raus, die AFD immer scheiße finden
```

## Rename Vars for sem
```{r}

# DF$semdat %<>% rename(x1 = kp10_160p, x2 = kp12_160p, x3 = kp14_160p, x4 = kp15_160p, x5 = kp16_160p,
#                       y1 = kp10_430i, y2 = kp12_430i, y3 = kp14_430i, y4 = kp15_430i, y5 = kp16_430i)
DF$semdat %<>% rename(x1 = kp21_160p1, x2 = kp23_160p1, x3 = kp24_160p1,
                      y1 = kp21_430i,  y2 = kp23_430i,  y3 = kp24_430i,
                      z1 = kp21_160p2, z2 = kp23_160p2, z3 = kp24_160p2)
# DF$semdat %<>% rename(z1 = kp15_1500)
```


## Check Correlations
```{r}
DF$semdat %>% 
  psych::cor.plot(.,stars = T)
# DF$semdat %>% select(ends_with(c("_160p","_430i"))) %>% 
#   gather(key, value) %>% drop_na() %>%
#   separate_wider_delim(key, delim = "_", names = c("Welle", "Var")) %>%
#   ggplot(aes(x = value, color = Welle)) +
#   geom_density(adjust = 1.6) +
#   facet_wrap(vars(Var)) +
#   theme_classic()

```

## Check ICC
```{r}
# ICC requires VARs to be numeric, even when they seem to are numeric -> mutate!

DF$semdat %>% 
  select(contains(c("x"))) %>% irr::icc()
DF$semdat %>%
  select(contains(c("y"))) %>% irr::icc()
DF$semdat %>%
  select(contains(c("z"))) %>% irr::icc()
```

# SEM
## Estimate Models
```{r Estimate Models}
tic()
DF$lv_mod$cl$m3c <- lavaan(DF$modef$cl$m3c, data=DF$semdat, missing="ML", estimator = "MLR", meanstructure = T, int.ov.free = T)
DF$lv_mod$cl$m3u <- lavaan(DF$modef$cl$m3u,  data=DF$semdat, missing="ML", estimator = "MLR", meanstructure = T, int.ov.free = T)
DF$lv_mod$ri$m3c <- lavaan(DF$modef$ri$m3c, data=DF$semdat, missing="ML", estimator = "MLR", meanstructure = T, int.ov.free = T)
DF$lv_mod$ri$m3u <- lavaan(DF$modef$ri$m3u,  data=DF$semdat, missing="ML", estimator = "MLR", meanstructure = T, int.ov.free = T)
DF$lv_mod$ri$m33u <- lavaan::sem(DF$modef$ri$m33u,  data=DF$semdat, missing="ML", estimator = "MLR", meanstructure = T, int.ov.free = T)
toc()
```

## Compare Model Fit
```{r Model fit}
CL_Modell = c("CLPM 3 fixed","CLPM 3 free")
RI_Modell = c("RI-CLPM 3 fixed","RI-CLPM 3 free")
map(DF$lv_mod$cl, broom::glance) %>% list_rbind() %>% select(c(cfi,tli,agfi,rmsea,srmr,AIC,BIC)) %>% cbind(CL_Modell,.) %>% 
  gt %>%
  fmt_number(decimals = 3, columns = c(cfi,tli,agfi,rmsea,srmr)) %>% gt_theme_nytimes()
map(DF$lv_mod$ri, broom::glance) %>% list_rbind() %>% select(c(cfi,tli,agfi,rmsea,srmr,AIC,BIC)) %>% cbind(RI_Modell,.) %>% 
  gt %>%
    fmt_number(decimals = 3, columns = c(cfi,tli,agfi,rmsea,srmr)) %>% gt_theme_nytimes()

```

## Graphs
```{r Prepare Graphs}
DF$cl_layout = openxlsx::read.xlsx(here("script/Clpm_t6_layout.xlsx")) %>%
  mutate(across(everything(), ~rec(., rec = "-99=NA;else = copy")))
DF$RI_layout = openxlsx::read.xlsx(here("script/RI-clpm_t6_layout.xlsx")) %>%
  mutate(across(everything(), ~rec(., rec = "-99=NA;else = copy")))

cl_graph_list <- map(DF$lv_mod$cl, function(model) {
  prepare_graph(model, layout = DF$cl_layout) %>%
    edit_graph({label_location = 0.8}, element = "edges") %>%
    edit_graph({ label = paste(est_sig_std)}, element="edges")
})  
ri_graph_list <- map(DF$lv_mod$ri, function(model) {
  prepare_graph(model, layout = DF$RI_layout) %>%
    edit_graph({label_location = 0.8}, element = "edges") %>%
    edit_graph({ label = paste(est_sig_std)}, element="edges")
})  
```

::: {.panel-tabset}
### CLPM 3 Wellen fixed
```{r}
plot(cl_graph_list$m3c)
```
### CLPM 3 Wellen free
```{r last cl graph}
plot(cl_graph_list$m3u)
```
:::

::: {.panel-tabset}
### RI-CLPM 3 Wellen fixed
```{r}
plot(ri_graph_list$m3c)
```
### RI-CLPM 3 Wellen free
```{r}
plot(ri_graph_list$m3u)
```
:::

## Coefficients

```{r Define Tables}

cl_crosslagged = DF$lv_mod$cl %>%  map(., function(x) {
  tidy_output <- broom::tidy(x) %>% filter(.,op =="~" & grepl("Lx", term) & grepl("Ly", term)) %>% 
  select(., c(term, op, estimate,std.error,p.value,std.all)) %>% gt %>% 
  fmt_number(decimals = 2, columns = c(estimate,std.error,std.all)) %>% fmt_number(decimals = 3, columns = p.value) %>%
  tab_style(style = cell_fill(color = "lightgreen"), locations = cells_body(columns = c(term,estimate,std.all), rows = p.value < 0.05)) %>%
  gt_theme_nytimes()
  return(list(tidy_output)) 
})


ri_crosslagged = DF$lv_mod$ri %>%  map(., function(x) {
  tidy_output <- broom::tidy(x) %>% filter(.,op =="~" & grepl("Lx", term) & grepl("Ly", term)) %>% 
  select(., c(term, op, estimate,std.error,p.value,std.all)) %>% gt %>% 
  fmt_number(decimals = 2, columns = c(estimate,std.error,std.all)) %>% fmt_number(decimals = 3, columns = p.value) %>%
  tab_style(style = cell_fill(color = "lightgreen"), locations = cells_body(columns = c(term,estimate,std.all), rows = p.value < 0.05)) %>%
  gt_theme_nytimes()
  return(list(tidy_output)) 
})


# broom::tidy(DF$lv_mod$ri$m5cv) %>% filter(.,op =="~" & grepl("Lx", term) & grepl("Ly", term)) %>% 
#   select(., c(term, op, estimate,std.error,p.value,std.all)) %>% gt %>% 
#   fmt_number(decimals = 2, columns = c(estimate,std.error,std.all)) %>% fmt_number(decimals = 3, columns = p.value) %>%
#   tab_style(style = cell_fill(color = "lightgreen"), locations = cells_body(columns = c(term,estimate,std.all), rows = p.value < 0.05)) %>%
#   gt_theme_nytimes()

```

::: {.panel-tabset}
### CLPM 3 Wellen fixed
```{r}
cl_crosslagged$m3c[[1]]
```
### CLPM 3 Wellen free
```{r}
cl_crosslagged$m3u[[1]]
```
:::


::: {.panel-tabset}
### RI-CLPM 3 Wellen fixed
```{r}
ri_crosslagged$m3c[[1]]
```
### RI-CLPM 3 Wellen free
```{r}
ri_crosslagged$m3u[[1]]
```
:::