---
title: "GLES Panel 2017-2021"
subtitle: "Wahlwerbung & Wahlabsicht"
author:
- "Reimar ZEH"
- "[Lehrstuhl für Kommunikationswissenschaft](https://www.kowi.rw.fau.de)"
- "Filename: *Recode ZA6838-ZA7729*"
date: "`r format(Sys.time(), '%m.%d.%Y')`"
editor: source
toc: true
number-sections: true
highlight-style: pygments
theme: cosmo
format:
  html: 
    code-fold: true
    code-overflow: wrap
    html-math-method: katex
    self-contained: true
    fig-width: 8
    fig-height: 6
execute: 
  echo: false
  eval: true
  warning: false
editor_options: 
  chunk_output_type: console
---
::: {.hidden}
# Session Setup  {.unnumbered .unlisted}
## Global settings & Notes
```{r}
rm(list= ls()) # start clean ####
# show chunk outputs in R-Markdown
knitr::opts_chunk$set(echo = TRUE)

# global settings
options(
  scipen = 999, # deactivate scientific notation
  digits = 3) # activate the required number of decimal places
```

## Load Packages

```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(sjlabelled,foreign,tidyverse,sjmisc,Hmisc,flextable,gt,gtExtras,
               here,fs,usethis,labelled,janitor,magrittr,qs,tictoc,
               psych,easystats,irr,lavaan,semTools,semPlot,broom,tidySEM,GPArotation)
```
:::


# Prepare Analysis
## Load Data

```{r}
# load(paste0(Sys.getenv("FAUBOX"),"/GLES/za6838/za6838_7729.Rda"))
# tic()
orgdat = qread(here("data/za6804_v7.qs"))
# za6804v7 = qread(paste0(Sys.getenv("FAUBOX"),"/GLES/za6838/za6804_v7.qs"))
source(here("ps_models.R"))
# toc()
```

## Select Vars
```{r}
semdat = orgdat %>% select(starts_with(c("kp5_421","kp6_421","kp7_421","kp5_170","kp6_170","kp7_170")) &
                                   !contains(c("_1701","_1702")) & !contains("flag") & !ends_with("y"))

semdat %<>% mutate(across(ends_with("_170"), ~rec(., rec = "-99,-97,-95,-93,-92=NA;6=1;else = copy")),
                     across(contains("_421"), ~rec(., rec = "-99,-97,-95,-93,-92=NA;else = copy")),
                     across(ends_with("_170"), ~rec(., rec = "rev")))

# semdat %<>% mutate(grp_age = dicho(alter, dich.by = 29))
```



## Prepare VARS
```{r}

for (i in 5:7) {
  varnames <- c("_421d", "_421e", "_421b", "_421g")
  colnames <- c("_wwtv", "_wwra", "_wwfl", "_wwpl")
  
  for (j in seq_along(varnames)) {
    varname <- paste0("kp", i, varnames[j])
    colname <- paste0("kp", i, colnames[j])
    semdat <- semdat %>% 
      mutate(!!colname := as.numeric(rowSums(across(contains(varname)), na.rm = F) > 0))
  }
  coltot <- paste0("kp", i, "_waw")
  vartot <- paste0("kp", i, "_ww")
  semdat <- semdat %>% 
    mutate(!!coltot := rowSums(across(contains(!!vartot)), na.rm = F))
}
```

## Check reliability
```{r}
#| results: asis
reli = list()
wellen <- c("kp5", "kp6", "kp7")
for (j in seq_along(wellen)) {
  reli_obj <- paste0("reli_", wellen[j])
  reli[[reli_obj]] = semdat %>% select(contains("_ww") & starts_with(wellen[j])) %>% psych::alpha(., na.rm = TRUE, check.keys = TRUE, warnings = FALSE)
}
reli %>% map(., ~gt(.$total) %>% gt_theme_nytimes())
reli %>% map(., ~rownames_to_column(.$alpha.drop, "ITEM") %>% gt() %>% 
                  tab_style(style = cell_text(color = "red", weight = "bold"), locations = cells_body(columns = ITEM, rows = std.alpha > 0.7 )))


```


## Rename, select & delete VARS
```{r}
semdat %<>% rename(x1 = kp5_170, x2 = kp6_170, x3 = kp7_170,
                     y1 = kp5_waw, y2 = kp6_waw, y3 = kp7_waw)
semdat %<>% select(starts_with(c("x","y")))
```

## Check ICC All cases
Wahlbeteiligungsabsicht
```{r}
# ICC requires VARs to be numeric, even when they seem to are numeric -> mutate!
semdat %>% select(contains(c("x"))) %>% 
                         irr::icc()
```
Wahlwerbungskontakte
```{r}
semdat %>% select(contains(c("y"))) %>% 
                         irr::icc()
```



# SEM
::: {.callout-important}
Lx(n) steht für die latenten Variablen der Wahlbeteiligungsabsicht der Wellen 5-7<br>
Ly(n) steht für die latenten Variablen der Wahlwerbungskontakte der Wellen 5-7<br>
Operationalisierung analog zu Schulz 2022,
:::

## CLPM free All cases listwise
```{r}
#| warning: false
tic()
sem.fit <- lavaan::sem(clpm_L, data=semdat, missing="listwise", estimator = "MLR", mimic="Mplus", meanstructure = T)
broom::glance(sem.fit) %>% 
  select(., c(cfi,tli,agfi,rmsea,srmr,estimator,nobs,norig,missing_method,ngroups)) %>% 
  gt()%>% fmt_number(decimals = 3) %>% gt_theme_nytimes()
broom::tidy(sem.fit) %>% filter(., op =="~") %>% 
  select(., c(term, op, estimate,std.error,p.value,std.all)) %>% gt() %>% 
  tab_style(style = cell_fill(color = "lightgreen"),
            locations = cells_body(columns = c(term,std.all), rows = p.value < 0.05)) %>%
  fmt_number(decimals = 3) %>% gt_theme_nytimes()
cl_layout = openxlsx::read.xlsx(here("script/Clpm_t3_layout.xlsx")) %>%
  mutate(across(everything(), ~rec(., rec = "-99=NA;else = copy")))
cl_graph = prepare_graph(sem.fit, layout = cl_layout) %>% edit_graph({label_location = 0.8}, element = "edges") %>% edit_graph({ label = paste(est_sig_std)}, element="edges")
plot(cl_graph)
toc()
```


## RI-CLPM All Cases listwise
```{r}
#| warning: false
tic()
ric.fit <- lavaan::sem(riclpm, data=semdat, missing="listwise", estimator = "MLR", mimic="Mplus", meanstructure = T)
broom::glance(ric.fit) %>% 
  select(., c(cfi,tli,agfi,rmsea,srmr,estimator,nobs,norig,missing_method)) %>% 
  gt() %>% fmt_number(decimals = 3) %>% gt_theme_nytimes()
broom::tidy(ric.fit) %>% filter(., op =="~") %>% 
  select(., c(term, op, estimate,std.error,p.value,std.all)) %>% gt() %>% 
  tab_style(style = cell_fill(color = "lightgreen"),
            locations = cells_body(columns = c(term,std.all), rows = p.value < 0.05)) %>%
  fmt_number(decimals = 3) %>% gt_theme_nytimes()
RI_layout = openxlsx::read.xlsx(here("script/RI-clpm_t3_layout.xlsx")) %>%
  mutate(across(everything(), ~rec(., rec = "-99=NA;else = copy")))
ric_graph = prepare_graph(ric.fit, layout = RI_layout) %>% edit_graph({label_location = 0.8}, element = "edges") %>%edit_graph({ label = paste(est_sig_std)}, element="edges")
plot(ric_graph)
toc()
```